Placeholder Title... Something About Delegating Quantum Computations

### 2019-09-11 delegations.tex
Remove unnecessary detail in definition
Change wording

\begin{definition}
	A quantum delegation protocol has \emph{long output} if the output can have multiple bits. In this case, the verifier should end with a measurement result of the output register.
\end{definition}

>>>>

\begin{definition}
	A quantum delegation protocol has \emph{long output} if the output register contains multiple qubits.
\end{definition}
